Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-14 Draft/Draft.Rmd
Discussion

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@ollerton2017; MORE REFS?]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them (**Figures 3** and **4**).  However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest levels of pollination contribution to reproduction [@rodger2021] was the most probable on the generalist motif for plant positions.

The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the structure of network motifs but also the identity of the elements of their structure are influenced by ecological processes that determine under- and over-representation of the different motif combinations. In addition, we found that just 30% of the possible 5,3250 motif combinations took place. However, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@bascompte2013]. Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016]. However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016]. Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represent set of indirect interactions that do not take place in natural systems.

Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems.

---

4) Limitations (but keep it short and simple): FG are hard to describe, bias in sampling worldwide, …

Although functional groups can define

- FG hard to describe: https://doi.org/10.1093/aob/mcp031 and the fenster one

- Paper of Poisot 2020

5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
---

>>>>

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them. However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).

The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations. In addition, we found that just 30% of the possible 5,3250 motif combinations took place. As suggested by @simmons2020, exploring the proportion of competitive or facilitative relized indirect interactions is a necessesary next step to improve our understanding of the architecture of biodiversity [@bascompte2007]. In addition, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@jordano2003; @bascompte2013]. Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016]. However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016]. Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represented non-realized combinations of indirect interactions.

4th: Link ideas...

Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems [@dellinger2020].

Further, delimiting both floral visitors and plants with traits could help revealing more trait-matching processes across groups that are not captured when taxonomic rank is used. Another limitation is that our study just considers binary interactions (presence-absence) and does not account for the interaction strength between plant and pollinator species which is essential to understand pollinator impact upon plant reproduction [REF].

. However, the analysis of quantitative motifs have been just recently develop [@bmotifsimmons2019] and more work is needed to understand their ecological implications in mutualistic networks. Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015]. This biasis are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.

Final one: 
5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.
